Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
Removed extraneous bit of examples section

This section introduces the intuition behind the properties through a series
of examples. Existing stack safety enforcement work mostly refers directly to examples
of bad behavior that it prevents; we will argue that: \bcp{Not sure this
  enumeration is useful.}\apt{+1}

\begin{itemize}
\item examples that appear to violate stack safety violate at least one of our properties;
\item we do not find desireable behaviors that appear stack-safe yet violate our properties; and
\item our properties are testably implemented by stack safety micro-policies from the
  literature, and the micro-policies are not significantly more conservative
  (i.e., policy failstops usually correspond to imminent property violations).
\end{itemize}

We show our examples both in C syntax and in corresponding assembly code for a
simple two-address machine. The address of each instruction is shown to its left.
The assembly code reflects a simple compilation model in which
local variables are stored in the stack frame.
For the moment, arguments and return values are passed in registers.
The machine is word-addressed. The stack grows upward in
memory and {\tt \%sp} points to the first unused word above the top of the stack.
The {\tt call} and {\tt ret} instructions push and pop the return address from the stack,
implicitly adjusting the stack pointer.
At the right of each example, we show the layout of stack memory just before
the specified instruction is executed; each box represents a memory word, and
addresses increase to the right.

>>>>

This section introduces the intuition behind the properties through a series
of examples. We show our examples both in C syntax and in corresponding assembly code for a
simple two-address machine. The address of each instruction is shown to its left.
The assembly code reflects a simple compilation model in which
local variables are stored in the stack frame.
For the moment, arguments and return values are passed in registers.
The machine is word-addressed. The stack grows upward in
memory and {\tt \%sp} points to the first unused word above the top of the stack.
The {\tt call} and {\tt ret} instructions push and pop the return address from the stack,
implicitly adjusting the stack pointer.
At the right of each example, we show the layout of stack memory just before
the specified instruction is executed; each box represents a memory word, and
addresses increase to the right.
